---
title: "How to use snapedautilityR"
author: "Kyle Ahn, Dongxiao Li, Harry Chan"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to use snapedautilityR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

`snapedautilityR` an open-source library that generate useful function to kickstart EDA (Exploratory Data Analysis) with just a few lines of code. The system is built around quickly analyzing the whole dataset and providing a detailed report with visualization. Its goal is to help quick analysis of feature characteristics, detecting outliers from the observations and other such data characterization tasks.

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Import library

Here we will demonstrate how to use `snapedautilityR` package for your data science project.
```{r setup}
library(snapedautilityR)
```

## Sample data

We will be using the `penguins` data and `iris` data here.
```{r}
library(palmerpenguins)
head(penguins)
```
```{r}
head(iris)
```


## Plot Histograms

**Functionality**

This function detects outliers in the given list, plots histogram given numeric features of the input data frame, and plots bar charts for categorical features of the input data frame.

**Function inputs**

- df: dfFrame that to be used for the plot
- features: List of string feature names
- facet_column: Number of columns in Integer type for facet options


```{r fig.width=7, fig.height=4}
plot_histograms(penguins, c("species", "flipper_length_mm", "bill_length_mm", "body_mass_g", "island"), 3)
```

## Plot Correlation

**Functionality**

This function generates a pearson correlation plot for a list of numeric features in a given data frame.

**Function inputs**

- df: dfFrame that to be used for the plot
- features: List of string feature names

```{r fig.width=7, fig.height=4}
numerical_features <- c('Sepal.Length','Sepal.Width','Petal.Width')
plot_corr(iris, features = numerical_features)
```

## Detect Outliers

**Functionality**

This function detect outliers in the given list Returns a threshold value for the lower bound and upper bound of the outliers and Plot a violin plot of the observations.

**Function inputs**

- s: list of double that contains the data
- width: The width of ggplot. Default set to 150
- height: The height of ggplot. Default set to 150

```{r fig.width=7, fig.height=4}
library(dplyr)
detect_outliers(pull(iris["Sepal.Length"]), 150, 150)
```
